On the discovery and origin of $r$-process stars in the Milky Way

### 2018-02-16 article/ms.tex
cant spell nobel prize without r-process enhancement

	\begin{abstract}
		The production of heavy elements occurs through the slow and rapid neutron capture process. Numerous sites satisfy the conditions needed for the r-process but the relative frequency of these sites is unknown, largely due to the lack of a large number of stars with strong r-process signatures. Here we report the discovery of 47 r-process enhanced stars discovered in the second LAMOST data release (DR2), more than doubling the known number in our Galaxy. After taking expected rates of core-collapse supernovae and the average r-process material ejected in each event, we find the core-collapse supernovae alone cannot explain the number of r-process stars discovered in this work. Current rate estimates of neutron-star mergers imply that should be about $\todo{X}$ r-process enhanced stars in the Milky Way, and about $\todo{Y}$ in LAMOST DR2. \todo{conclusions....}To our knowledge, this is the first work that links the rates of neutron-star mergers to the number of r-process stars in the Milky Way.
		% contrary to previous conclusions in the literature including all r-process material being produced in small amounts in common events such as core-collapse supernovae, or the material exclusively being produced in very large amounts in very rare events, such as neutron star mergers. 
	\end{abstract}

@@

	Heavy elements ($Z > 30$) are synthesised through the slow (s) and rapid (r) neutron capture processes \citep[e.g.,][]{Burbidge1957,Sneden2008}. 
	%Potential sites of the r-process have been discussed for over sixty years. 
	Rapid neutron capture occurs when the neutron density is high enough that the rate of neutron capture will occur faster than the rate at which the isotope undergoes a $\beta$-decay. Extremely high neutron densities (\todo{of how much}) are necessary for the r-process to occur. Sites meeting this criteria include core-collapse supernovae, neutron star mergers, or magnetorotationally driven supernovae. Core-collapse supernovae are relatively common throughout the Galaxy, but they only produce small amounts of r-process material. Neutron star mergers or magnetorotationally driven supernovae, however, occur much less frequently than core-collapse supernovae, but produce far more r-process material. Events such as these are theorised to account for the case of the highly r-process enhanced stars in the ultra-faint dwarf (UFD) galaxy Reticulum II \citep{Ji2016}. %Neutron star mergers may have a stronger argument to be the parent site of this level of r-process enhancement in such a small volume. However, magnetorotationally driven supernovae are also a possible solution.
Magnetorotationally driven supernovae may not produce as much r-process material as neutron star mergers (although still more than core-collapse supernovae), they are thought to occur more frequently than neutron-star mergers \todo{[citation needed]}, and the predicted abundance patterns make them observationally indistinguishable from neutron star mergers \citep{Ji2016}.

	Europium ($Z=63$) is entirely produced through the r-process. This makes it a very useful signature for identifying stars that show evidence of excess pollution by r-process material. %\todo{CLUMSY, lose the first half-sentence:The recent discovery of the UFD Reticulum II used Europium as evidence of its r-process enhancement, and found the particularly interesting result that the UFD's level of r-process enrichment was too high to have occurred through a core-collapse supernovae event.}
	Historically, UFD galaxies have demonstrated some of the lowest abundance ratios of r-process elements seen in the Milky Way or its satellite systems. However, the analysis of several of Reticulum II's stars show they are greatly enriched, 2-3 orders of magnitude higher than stars found in any other UFD galaxy \citep{Ji2016}. This degree of enrichment supports the theory that a single rare event must have occurred early on in the formation history of Reticulum II. This is supported by the observed heavy element yields, which are found to be some 1000 times higher than what is achievable on average from core-collapse supernovae ejecta. It is highly improbable that 1000 supernovae could have contributed to Reticulum II, suggesting that the r-process material must be produced by a rarer astrophysical event such as a binary neutron star merger.

	While neutron star mergers or magnetorotationally driven supernovae are likely to produce significant amounts of r-process material, it does not suggest that all r-process material stems from these sources either. Rather, the rarity of these events might imply that they are also responsible for the rare numbers of stars  observed to have significant enhancements in r-process material. One could ask if neutron-star mergers could be responsible for all r-process stars known in the Milky Way? On the other hand, if we assume very little gas mixing, could could core-collapse supernovae create enough material to explain a single r-process star? If neither of these prove to be true then we can confirm that there must be multiple sties to the r-process, providing a step forward in understanding the relative fraction of these mechanisms in the Milky Way.

%	 stars we've found? And if neither of these prove to be the case, can we then conclude that there must be multiple sites of r-process element creation throughout the Milky Way, that create these elements to different extents?
	In order to answer these questions it is necessary to identify a large sample of r-process stars.
	 However, r-process stars are very rare, which makes finding this stars difficult. For this reason we must look to massive data sets, such as the LAMOST sky survey. In this letter we report the discovery of 47 r-process enhanced stars identified from LAMOST.
	In Section 2 we outline the methods used to identify r-process enhanced candidates, and our analysis methods. In Section 3 we discuss what our results imply about the sites of r-process. We provide concluding remarks in Section 4.

@@

	\section{The r-process}
	% Repeating the introduction:
	%For the r-process to occur there must be a very high neutron density, such that neutron capture must be able to occur before the nucleus undergoes a $\beta$-decay (assuming the nucleus is in an unstable state). The conditions that can create this are rare. Events such as supernovae or neutron star mergers list among the most favoured sites.

@@

	The previous sample of r-process stars, before the release of this letter, almost exclusively consists of metal-poor stars \todo{[OMG CITATIONS NEEDED DUDE]}. This fact is not to be confused with saying that most r-process stars found should be metal-poor stars, rather that at low metallicities we know that the s-process will not contribute, so neutron capture elements formed from these stars would be only from the r-process. Over half the current known r-process stars are members of the ultra faint dwarf galaxy, Reticulum II. However, Europium we know to be totally made from the r-process, therefore even at metallicities where the s-process contributes, Europium is a valuable indicator of r-process synthesis.

	\subsection{Multiple r-process sites?}
	While it is possible that all currently known r-process enhancements can be made by neutron star mergers, we still observe stellar populations in the galaxy which show particularly weak enrichment from r-process elements ([Eu/Fe] < 0.7). These enhancements imply that an additional site of r-process element synthesis is likely to be active \todo{or there is very efficient mixing?? I think here you just want to say that either there is $>1$ r-process site, or there is extremely heterogeneous levels of mixing from neutron-star mergers in order to produce stars with [Eu/Fe] abundances that range many orders of magnitude...}.

	%As we show in \ref{rates}  neutron star merger rates may show that all heavily enriched stars can be enhanced by these phenomena within an adequate time-scale. However, we are not able to assume that as a consequence of the merger some stars are greatly enhanced, while others are only very slightly enhanced. It is more accurate to propose that at least two sites exist, with one (potentially mergers) producing a massive amount of enhanced material, and another only producing a small amount, such as supernovae.

@@

	From these two rates, we can for the first time to our knowledge, estimate the amount of r-process stars that should be present in the Milky Way, enhanced both by purely neutron star mergers and purely core-collapse supernovae. We do this assuming instant recycling, and that no r-process matter pollutes stars by any other means than these.

	From these rates we can find an estimate of how many r-process enhanced giants should be present from an approximate number of the Milky Way's total stars. As well as an estimate of how many enhanced stars, giants or otherwise, that should be present in the Milky Way.

@@

	We also state that a star is said to be enhanced if [Eu/Fe] $\geq$ 0.7, and performed the lower-bound estimate that all of our 47 stars exhibit this abundance. The amount of r-process material expelled by neutron star mergers is the same as previously discussed, using Europium as our identifier, of $M_{Eu}\approx10^{-4.5} M_{\odot}$.

    It was found that in the Milky Way there should be present 9,896 r-process enhanced stars from solely neutron star mergers. Taking into account that this should be considered a lower-bound estimate (by assuming a lower bound Europium abundance) this is a startlingly large difference from the known 60 r-process stars in the Milky Way.

@@

    We find that, by using the assumptions listed, neutron star mergers could create enough r-process material to enrich above the point of [Eu/Fe] > 0.7 for all 60 known r-process enhanced stars within $13.87\times10^9$ years, very close to the age of the universe. From our rates of core-collapse supernovae however, we find that the earliest time-scale at which they can create this level of r-process material is $3.1\times10^{11}$ years, not at all within the age of the universe. This illustrates, with our current knowledge of core-collapse supernovae frequency, and the amount of r-process material they eject, core-collapse supernovae cannot be the sole source of r-process enrichment in the Milky Way.

@@

    \todo{For Andy (haven't written this bit nicely this was a thought dump): Let us consider that both of these estimates are correct, and the rates they are based on have been roughly accurate over the age of the universe (although they should have increased with time, which is actually a bit worse for us). Then we are left with our previous prediction of 9,896 stars enhanced purely by neutron star mergers, and another 442 stars enhanced purely by core-collapse supernovae. This leaves us with a new sample of r-process enhanced stars that should exist in the Milky Way of 10,338. 
    At a rough estimate, the LAMOST data release 2 took spectra for 0.00088\% of the Milky Way's stars (assuming an average amount of stars in the Milky Way of 250 billion). In this very small percentage, 47 r-process enhanced stars were found. Then, if we are able to assume that there is nothing particularly special about the area of the sky that LAMOST surveyed, scaling this size to that of the Milky Way we should find 5,340,892 r-process enhanced stars. Clearly there is something wrong.}

	\section{Conclusions}
	We present the largest to date sample of r-process element enhanced stars to date. Our sample is found at a wide range of metallicities, contrary to previous discoveries that focussed on metal-poor r-process enhanced stars. Similarly they are not clumped in either temperatures, $log(g)$, or radial velocity. They don't cluster to any one end of the H-R diagram, highlighting no correlation between type of star, they are observed both in the disk and halo, and are not clustered anywhere in the sky. In addition to this we also present the first ever estimate to our knowledge, from information provided by advanced LIGO, that neutron star mergers possess the ability to synthesise all currently known r-process material in a feasible time-scale. We also provide evidence that we can confidently conclude core-collapse supernovae can not possibly be the only progenitors of r-process material in the Milky Way Galaxy.

@@

	\bibliographystyle{mnras}
	%\bibliography{paper} % if your bibtex file is called example.bib
	\begin{thebibliography}{99}
		\bibitem[\protect\citeauthoryear{Abbott, B.P. et al.}{2016}]{LIGO2016}
		Abbot B.P. et al. 2016, Living Reviews in Relativity, 19, 1
		\bibitem[\protect\citeauthoryear{Argast, D. et al.}{2004}]{Argast2004}
		Argast D., Samland M., Thielmann F-K. \& Qian Y-Z. 2004, Astronomy and Astrophysics, 416
		\bibitem[\protect\citeauthoryear{Burbidge, E. et al.}{1957}]{Burbidge1957}
		Burbidge E. M., Burbidge G. R., Fowler W. A., \& Hoyle F. 1957, Review of Modern Physics, 29, 4
		\bibitem[\protect\citeauthoryear{Burrows, A. et al.}{1995}]{Burrows1995}
		Burrows, A., Hayes, J., \& Fryxell, Bruce A. 1992, ApJ, 450, 830
		\bibitem[\protect\citeauthoryear{Drout, M. R. et al.}{2017}]{Drout2017}
		Drout, M. R. et al. 2017, Science
		\bibitem[\protect\citeauthoryear{Goriely, S. et al.}{2011}]{Goriely2011}
		Goriely S., Bauswein A. \& Janka H-T. 2011, , 738, L32
		\bibitem[\protect\citeauthoryear{Ho et al.}{2017}]{AnnaHo2017}
		Ho A. Y. Q., Ness M. K., Hogg David W., Rix H-W., Liu C., Yang F., Zhang Y., Hou Y.,\& Wang Y. 2017, ApJ, 836, 1
		\bibitem[\protect\citeauthoryear{Hotokezaka, K. et al.}{2013}]{Hotok2013}
		Hotokezaka, K., Kiuchi, K., Kyutoku, K., Okawa, H., Skiguchi, Y., Shibata, M., \& Taniguchi, K. 2013, APS
		\bibitem[\protect\citeauthoryear{Ji, A. P. et al.}{2016}]{Ji2016}
		Ji A. P., Frebel A., Chiti A., \& Simon J. D. 2016, Nature, 531
		\bibitem[\protect\citeauthoryear{Kasen, D. et al.}{2017}]{Kasen2017}
		Kasen, D., Metzger, B., Barnes, J., Quataert, E., \& Ramirez-Ruiz, E. 2017, Nature, 551, 7678
		\bibitem[\protect\citeauthoryear{Li, W. et al.}{2011}]{Li2011}
		Li, W., Chornock, R., Leaman, J., Filippenko, A. V., Poznanski, D., Wang, X., Ganshalingam, M., \& Mannucci, F. 2011, Royal Astronomical Society, 412, 1473
		\bibitem[\protect\citeauthoryear{Sneden, C. et al.}{2008}]{Sneden2008}
		Sneden C., Cowan J.J., \& Gallino R. 2013, Annual review of Astronomy \& Astrophysics, 46, 1
		\bibitem[\protect\citeauthoryear{Woosley, S.E. et al.}{1992}]{Woosley1992}
		Woosley S.E, \& Hoffman R.D. 1992, ApJ, 395, 1
	\end{thebibliography}

>>>>

	\begin{abstract}
		The production of heavy elements occurs through the slow and rapid neutron capture process. Numerous sites satisfy the conditions needed for the r-process but the relative frequency of these sites is unknown, largely due to the lack of a large number of stars with strong r-process signatures. Here we report the discovery of 47 r-process enhanced stars discovered in the second LAMOST data release (DR2), more than doubling the known number in our Galaxy. After taking expected rates of core-collapse supernovae and the average r-process material ejected in each event, we find the core-collapse supernovae alone cannot explain the number of r-process stars discovered in this work. Current rate estimates of neutron-star mergers imply that should be about $9896$ r-process enhanced stars in the Milky Way, and about $0.087$ in LAMOST DR2. We find that neutron star mergers are also able to create all currently known r-process enhanced stars within a reasonable timescale. Additionally these 47 stars show no correlation to poor metallicity, providing evidence against the relationship of poor metallicity environments and the action of the r-process.
		To our knowledge, this is the first work that links the rates of neutron-star mergers to the number of r-process stars in the Milky Way.
	\end{abstract}

@@

	Heavy elements ($Z > 30$) are synthesised through the slow (s) and rapid (r) neutron capture processes \citep[e.g.,][]{Burbidge1957,Sneden2008}.
	Rapid neutron capture occurs when the neutron density is high enough that the rate of neutron capture will occur faster than the rate at which the isotope undergoes a $\beta$-decay. Extremely high neutron densities ($>10^{24}\ \rm{free\ neutrons\ per\ cm}^{3}$) \citep[e.g.,][]{Burbidge1957,Sneden2008} are necessary for the r-process to occur. Sites meeting this criteria include core-collapse supernovae, neutron star mergers, or magnetorotationally driven supernovae. Core-collapse supernovae are relatively common throughout the Galaxy, but they only produce small amounts of r-process material. Neutron star mergers or magnetorotationally driven supernovae, however, occur much less frequently than core-collapse supernovae, but produce far more r-process material. Events such as these are theorised to account for the case of the highly r-process enhanced stars in the ultra-faint dwarf (UFD) galaxy Reticulum II \citep{Ji2016}.
	Magnetorotationally driven supernovae may not produce as much r-process material as neutron star mergers (although still more than core-collapse supernovae), they are thought to occur more frequently than neutron-star mergers \citep[e.g.,][]{Li2011, LIGO2016}, and the predicted abundance patterns make them observationally indistinguishable from neutron star mergers \citep{Ji2016}.

	Europium ($Z=63$) is entirely produced through the r-process. This makes it a very useful signature for identifying stars that show evidence of excess pollution by r-process material. Using Europium, Reticulum II found the particularly interesting result that the UFD's level of r-process enrichment was too high to have occurred through a core-collapse supernovae event.
	Historically, UFD galaxies have demonstrated some of the lowest abundance ratios of r-process elements seen in the Milky Way or its satellite systems. However, the analysis of several of Reticulum II's stars show they are greatly enriched, 2-3 orders of magnitude higher than stars found in any other UFD galaxy \citep{Ji2016}. This degree of enrichment supports the theory that a single rare event must have occurred early on in the formation history of Reticulum II. This is supported by the observed heavy element yields, which are found to be some 1000 times higher than what is achievable on average from core-collapse supernovae ejecta. It is highly improbable that 1000 supernovae could have contributed to Reticulum II, suggesting that the r-process material must be produced by a rarer astrophysical event such as a binary neutron star merger.

	While neutron star mergers or magnetorotationally driven supernovae are likely to produce significant amounts of r-process material, it does not suggest that all r-process material stems from these sources either. Rather, the rarity of these events might imply that they are also responsible for the rare numbers of stars  observed to have significant enhancements in r-process material. One could ask if neutron-star mergers could be responsible for all r-process stars known in the Milky Way? On the other hand, if we assume very little gas mixing, could core-collapse supernovae create enough material to explain a single r-process star? If neither of these prove to be true then we can confirm that there must be multiple sties to the r-process, providing a step forward in understanding the relative fraction of these mechanisms in the Milky Way.

	In order to answer these questions it is necessary to identify a large sample of r-process stars.
	However, r-process stars are very rare, which makes finding this stars difficult. For this reason we must look to massive data sets, such as the LAMOST sky survey. In this letter we report the discovery of 47 r-process enhanced stars identified from LAMOST, significantly building upon the previously known Milky Way sample of 14 \citep[e.g.,][]{masho2011,Honda2004,Hayek2009,Sneden2003,Ivans2006,Hill2002,Christlieb2004,Wako2010,placo2017}.
	In Section 2 we outline the methods used to identify r-process enhanced candidates, and our analysis methods. In Section 3 we discuss what our results imply about the sites of r-process. We provide concluding remarks in Section 4.

@@

	\section{Identifying the r-process}

@@

	The previous sample of r-process stars, before the release of this letter, almost exclusively consists of metal-poor stars \citet{Barklem2005}. This fact is not to be confused with saying that most r-process stars found should be metal-poor stars, rather that at low metallicities we know that the s-process will not contribute, so neutron capture elements formed from these stars would be only from the r-process. Over half the current known r-process stars are members of the ultra faint dwarf galaxy, Reticulum II. However, Europium we know to be totally made from the r-process, therefore even at metallicities where the s-process contributes, Europium is a valuable indicator of r-process synthesis.

	\subsection{Multiple r-process sites?}
	While it is possible that all currently known r-process enhancements can be made by neutron star mergers (we show this in Section \ref{rates}), we still observe stellar populations in the galaxy which show particularly weak enrichment from r-process elements ([Eu/Fe] < 0.7). These enhancements imply either that there is more than $1$ active r-process site, or that there is present very heterogeneous levels of mixing, such that neutron-star mergers are able to enhance stars with [Eu/Fe] abundances that range many orders of magnitude.

@@

	From these two rates, we can for the first time to our knowledge, estimate the amount of r-process giants that should be present in the Milky Way, enhanced both by purely neutron star mergers, and purely core-collapse supernovae. As well as an estimate of how many enhanced stars, giants or otherwise, that should be present in the Milky Way. We do this assuming instant recycling, and that no r-process matter pollutes stars by any other means than these.

@@

	We also state that a star is said to be enhanced if [Eu/Fe] $\geq$ 0.7, and performed the lower-bound estimate that all of our 47 stars exhibit this abundance. The amount of r-process material expelled by neutron star mergers is the same as previously discussed, using Europium as our tracer, of $M_{Eu}\approx10^{-4.5} M_{\odot}$.

	These calculations were achieved by finding a density, $\rho$, such that:
	\begin{center}
	$\rho$ = $M_{Ejecta}*\rm{Rate}*13.8*10^{9}$
	\end{center}
	Where 'Rate' is defined as the number of neutron-star mergers that occur per parsec, per year.

	The total known mass of Europium exhibited in these 47 stars was then calculated:
	\begin{center}
	$Eu_{\rm{Mass}} = 47*Eu_{\rm{Atomic\ mass}}*N_{\rm{Eu atoms}}$\\\\
	\end{center}
	Where:
	\begin{center}
	$Eu_{\rm{Atomic\ mass}} = 2.52342^{-25}$ and;\\\\
	$N_{\rm{Eu\ atoms}} = 10^{[Eu/H]-12} \times N_{\rm{Hydrogen\ atoms}}$\\
	\end{center}
	Where the number of Hydrogen atoms was approximated from the Hydrogen atomic mass and the assumption that a giant star will be composed of $\approx$75\% Hydrogen and will have a mass of $\approx 0.8\ M_{\odot}$

    It was found that in the Milky Way there should be present 9,896 r-process stars enhanced solely from neutron star mergers. Taking into account that this should be considered a lower-bound estimate (by assuming a lower bound Europium abundance) this is a startlingly large difference from the known 61 r-process stars in the Milky Way.

@@

    We find that, by using the assumptions listed, neutron star mergers could create enough r-process material to enrich above the point of [Eu/Fe] > 0.7 for the 47 known r-process enhanced stars within the LAMOST sample within $10.87\times10^9$ years, very close to the age of the universe. From our rates of core-collapse supernovae however, we find that the earliest time-scale at which they can create this level of r-process material is $2.4\times10^{11}$ years, not at all within the age of the universe. This illustrates, with our current knowledge of core-collapse supernovae frequency, and the amount of r-process material they eject, core-collapse supernovae cannot be the sole source of r-process enrichment in the Milky Way.

@@

    In an effort to confirm this, we approached the calculation from a different direction. Were we to take our sample of 47 giants found in the LAMOST data, and increase it to the full estimated amount of giants in the galaxy (75,300,000), then we would expect to find 7849 enhanced giant stars, very close to 9896 stars from the previous calculation.

	\section{Conclusions}
	We present the largest to date sample of r-process element enhanced stars to date. Our sample is found at a wide range of metallicities, contrary to previous discoveries that focussed on metal-poor r-process enhanced stars. These 47 stars represent the first r-process enhanced stars found at [Eu/Fe] $>-2$. They are not clumped in either temperatures, log(g), or radial velocity. They don't cluster to any one end of the H-R diagram, highlighting no correlation between type of star, they are observed both in the disk and halo, and are not clustered anywhere in the sky. In addition to this we also present the first ever estimate to our knowledge, from information provided by advanced LIGO, that neutron star mergers possess the ability to synthesise all currently known r-process material in a feasible time-scale. We also provide evidence that we can confidently conclude core-collapse supernovae can not possibly be the only progenitors of r-process material in the Milky Way Galaxy.

@@

	\bibliographystyle{mnras}
	%\bibliography{paper} % if your bibtex file is called example.bib
	\begin{thebibliography}{99}
		\bibitem[\protect\citeauthoryear{Abbott, B.P. et al.}{2016}]{LIGO2016}
		Abbot B.P. et al. 2016, Living Reviews in Relativity, 19, 1
		\bibitem[\protect\citeauthoryear{Argast, D. et al.}{2004}]{Argast2004}
		Argast D., Samland M., Thielmann F-K. \& Qian Y-Z. 2004, Astronomy and Astrophysics, 416
		\bibitem[\protect\citeauthoryear{Barklem, P.S. et al.}{2005}]{Barklem2005}
		Barklem, P.S., Christlieb, N., Beers, T.C., Hill, V., Besel, M.S., Holmberg, J., Marsteller, B., Rossi, S., Zickgraf, F.-J. \& Reimers, D. 2005, A\&A, 439, 1
		\bibitem[\protect\citeauthoryear{Burbidge, E. et al.}{1957}]{Burbidge1957}
		Burbidge E. M., Burbidge G. R., Fowler W. A., \& Hoyle F. 1957, Review of Modern Physics, 29, 4
		\bibitem[\protect\citeauthoryear{Burrows, A. et al.}{1995}]{Burrows1995}
		Burrows, A., Hayes, J., \& Fryxell, Bruce A. 1992, ApJ, 450, 830
		\bibitem[\protect\citeauthoryear{Cui, X.-Q. et al.}{2012}]{lamost}
		Cui, X.-Q. et al., Research in Astronomy and Astrophysics, 12, 9
		\bibitem[\protect\citeauthoryear{Drout, M. R. et al.}{2017}]{Drout2017}
		Drout, M. R. et al. 2017, Science
		\bibitem[\protect\citeauthoryear{Christlieb N. et al.}{2004}]{Christlieb2004}
		Christlieb N. et al. 2004, Astronomy \& Astrophysics, 428, 1
		\bibitem[\protect\citeauthoryear{Goriely, S. et al.}{2011}]{Goriely2011}
		Goriely S., Bauswein A. \& Janka H-T. 2011, , 738, L32
		\bibitem[\protect\citeauthoryear{Hayek, W. et al.}{2009}]{Hayek2009}
		Hayek W., Wiesendahl U., Christlieb N., Eriksson K., Barklem P. S., Hill V., Beers T. C., Farouqi K., Pfeiffer B.,\& Kratz K.-L. 2009, Astronomy and Astrophysics, 504, 1
		\bibitem[\protect\citeauthoryear{Hill, V. et al.}{2002}]{Hill2002}
		Hill V. et al. Astronomy \& Astrophysics, 387, 1
		\bibitem[\protect\citeauthoryear{Ho et al.}{2017}]{AnnaHo2017}
		Ho A. Y. Q., Ness M. K., Hogg D. W., Rix H-W., Liu C., Yang F., Zhang Y., Hou Y.,\& Wang Y. 2017, ApJ, 836, 1
		\bibitem[\protect\citeauthoryear{Honda S. et al.}{2004}]{Honda2004}
		Honda S., Aoki W., Kajino T., Ando H., Beers T. C., Izumiura H., Sadakane K. \& Takada-Hidai M. 2004, ApJ, 607, 1
		\bibitem[\protect\citeauthoryear{Hotokezaka, K. et al.}{2013}]{Hotok2013}
		Hotokezaka K., Kiuchi K., Kyutoku K., Okawa H., Skiguchi Y., Shibata M., \& Taniguchi K. 2013, APS
		\bibitem[\protect\citeauthoryear{Ivans, I. I. et al.}{2006}]{Ivans2006}
		Ivans I. I.,Simmerer J., Sneden C., Lawler J. E., Cowan J. J., Gallino R., \& Bisterzo S. 2006, ApJ, 645, 1
		\bibitem[\protect\citeauthoryear{Ji, A. P. et al.}{2016}]{Ji2016}
		Ji A. P., Frebel A., Chiti A., \& Simon J. D. 2016, Nature, 531
		\bibitem[\protect\citeauthoryear{Kasen, D. et al.}{2017}]{Kasen2017}
		Kasen D., Metzger B., Barnes J., Quataert E., \& Ramirez-Ruiz E. 2017, Nature, 551, 7678
		\bibitem[\protect\citeauthoryear{Lai, D. K. et al.}{2008}]{Lai2008}
		Lai D. K., Bolte M., Johnson J. A., Lucatello S., Heger A., \& Woosley S. E. 2008, ApJ, 681,
		\bibitem[\protect\citeauthoryear{Li, W. et al.}{2011}]{Li2011}
		Li W., Chornock R., Leaman J., Filippenko A. V., Poznanski D., Wang X., Ganshalingam M., \& Mannucci F. 2011, Royal Astronomical Society, 412, 1473
		\bibitem[\protect\citeauthoryear{Majewski, S.R., et al.}{2017}]{apogee}
		Majewski S.R., et al., The Astronomical Journal, 154, 3
		\bibitem[\protect\citeauthoryear{Mashonkina, L., et al.}{2010}]{masho2011}
		Mashonkina L., Christlieb N., Barklem P.S., Hill V., Beers T.C., \& Velichko A., Astronomy and Astrophysics, 516, 46
		\bibitem[\protect\citeauthoryear{Placco, V.M., et al.}{2017}]{placo2017}
		Placco V.M., Holmbeck E. M., Frebel A., Beers T. C., Surman R. A., Ji A. P., Ezzeddine R., Points S. D., Kaleida C. C. Hansen T. T., Sakari C. M, \& Casey A. R., ApJ, 844, 1
		\bibitem[\protect\citeauthoryear{Sneden, C. et al.}{2008}]{Sneden2008}
		Sneden C., Cowan J.J., \& Gallino R. 2008, Annual review of Astronomy \& Astrophysics, 46, 1
		\bibitem[\protect\citeauthoryear{Sneden, C. et al.}{2003}]{Sneden2003}
		Sneden C. et al. 2003, ApJ, 591, 2
		\bibitem[\protect\citeauthoryear{Wako, A. et al.}{2010}]{Wako2010}
		Wako A., Beers T. C., Honda S. \& Carollo D. 2010, ApJ, 723, 1
		\bibitem[\protect\citeauthoryear{Woosley, S.E. et al.}{1992}]{Woosley1992}
		Woosley S.E, \& Hoffman R.D. 1992, ApJ, 395, 1
	\end{thebibliography}
